Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-26 Methods-and-Results.tex
ml coeff latex fix

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
interaction with a non-Dutch (which did not relate to outgroup attitudes
independently; For full results see Online Supplementary Materials
B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance. This is unusual because this might indicate the the effect is very consistent across participants. However, this might also be the case due to a small number of participants, or other measurement issues.}.
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants,
keeping in mind that the between-participant analyses in the aggregated
form are based in a small sample size.

@@

t be explained by whether or not the interaction fulfilled the person's
core situational need. This should, in turn, be due to a higher
perceived interaction quality. We will this sequentially test whether
the fulfillment of the core need during an interaction is (1) related to
more positive outgroup attitudes, (2) higher perceived interaction
quality, and (3) whether the variance explained by the core need is
assumed by the perceived interaction quality if considered jointly.

\begin{itemize}
\tightlist
\item
  Att \textasciitilde{} Need \& Qlt \textasciitilde{} Need
\item
  Att \textasciitilde{} Need + Qual
\end{itemize}

>>>>

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
t(1200) = 4.36, \textit{p} = \textless{} .001,
\textbackslash textit\{95\%CI{[}1.36, 3.59{]}), even after controlling
for having an interaction with a non-Dutch (which did not relate to
outgroup attitudes independently; For full results see Online
Supplementary Materials
B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance. This is unusual because this might indicate the the effect is very consistent across participants. However, this might also be the case due to a small number of participants, or other measurement issues.}.
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants,
keeping in mind that the between-participant analyses in the aggregated
form are based in a small sample size.

@@

The main proposal of our article is that the success of an outgroup
interaction might be explained by whether or not the interaction
fulfilled the person's core situational need. This should, in turn, be
due to a higher perceived interaction quality. We will this sequentially
test whether the fulfillment of the core need during an interaction is
(1) related to more positive outgroup attitudes, (2) higher perceived
interaction quality, and (3) whether the variance explained by the core
need is assumed by the perceived interaction quality if considered
jointly.

We find that in the highest multilevel models, the fulfillment of core
situational needs during outgroup contacts was associated with more
positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
t(365) = 2.93, \textit{p} = = 0.004,
\textbackslash textit\{95\%CI{[}0.06, 0.30{]}) and also predicted higher
perceived interaction quality (random intercept model; \textit{b} =
0.42, t(365) = 8.07, \textit{p} = \textless{} .001,
\textbackslash textit\{95\%CI{[}0.32, 0.52{]}). However, if we consider
the influences of core need fulfillment and interaction quality on
outgroup attitudes jointly, we find that virtually all variance is
explained by perceived interaction quality (random slopes mode;
\textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
\textbackslash textit\{95\%CI{[}0.12, 0.33{]}) and only little unique
variance is still explained by core need fulfillment (\textit{b} = 0.04,
t(364) = 0.64, \textit{p} = = 0.523,
\textbackslash textit\{95\%CI{[}-0.08, 0.15{]}). We thus find support
for our hypotheses and can conclude that in this data set the
fulfillment of core situational needs had a significant influence on
outgroup attitudes and that this effect is likely explained by its
effect through perceived interaction quality.

\faQuestionCircle~Are we sure that we don't want some sort of
bootstrapped indirect effect?
